### 2016-03-31 chapters/concept.tex
minor fixes
table corrected

Another error we found is one or more features having a parent feature which doesn't exist as a code artifact itself. Thus, the parent feature doesn't exists in the feature model and it's child features can't be placed in the hierarchy in the correct place. To still include these features in the feature model we create an {\color{red}abstract feature (Zitat: fospl, page 35, line 10)} for the parent feature. The abstract feature is a direct child of the root feature. As it doesn't have any describing code, it only has a name and no additional descriptive details.

@@

\begin{figure}[H]
\begin{tabulary}{\linewidth}{LLL}
\textbf{Tag} & \textbf{attributes} & \textbf{child tags}\\
\hline
configurationSurvey & & projectName, section, page\\
section & id & name, description\\
page & id, sectionId & question, answers\\
answers & type & answer\\
answer & nextPageId & label, description, dependencies\\
dependencies & & feature\\
feature & selection & \\
\end{tabulary}\vspace{2.5em}
\end{figure}

>>>>

%Cite: fospl, page 35, line 10
Another error we found is one or more features having a parent feature which doesn't exist as a code artifact itself. Thus, the parent feature doesn't exists in the feature model and it's child features can't be placed in the hierarchy in the correct place. To still include these features in the feature model we create an abstract feature \cite{fospl} for the parent feature. The abstract feature is a direct child of the root feature. As it doesn't have any describing code, it only has a name and no additional descriptive details.

@@

\begin{figure}[H]
\begin{tabulary}{\linewidth}{| L | L | L |}
	\hline
	\textbf{Tag} 		& \textbf{\mbox{Attributes}} & \textbf{Child tags}	\\ \hline

	configurationSurvey & 				& projectName, section, page		\\ \hline
	section 			& id 			& name, description					\\ \hline
	page 				& id, sectionId & question, answers					\\ \hline
	answers 			& type 			& answer							\\ \hline
	answer 				& nextPageId 	& label, description, dependencies	\\ \hline
	dependencies		& 				& feature							\\ \hline
	feature 			& selection 	& 									\\ \hline
\end{tabulary}
\caption{Table with the XML element structure}
\label{tab-xmlelements}
\end{figure}
